Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2025-01-17 main.tex
some clean up and new writing

We compare the reference Neumann eigenvalues with the gradient potential estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
A brufe-force search easily enumerates all the shortest face-paths that start from a given triangle, so we use the best possible estimate that this method provides.

We compare the reference Neumann and Dirichlet eigenvalues with the bounds in Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
Here, we take into account Lemma~\ref{lemma:volumecomparison} and Theorem~\ref{proposition:starreflection} (with Remark~\ref{remark:improved_starreflection}).
Again, brute-force search is feasible to enumerate all possible shellings of moderately small two-dimensional triangulations,
so the best possible estimate with that method can be obtained.

@@

The reference Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators are found via standard finite element eigenvalue computations, using the lowest-order finite element de~Rham complex and a sufficiently refined mesh (four steps of uniform refinement).
As in the two-dimensional case outlined above, we again compare these reference values with estimates obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad}, Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}, and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.

Enumerating all the shortest-path trees of the triangulations above is feasible but takes considerably longer. 
Brute-force enumeration of all shellings seems infeasible, though. 
Instead,

\todo{1. be explicit whether/that a shortest path tree is needed. 2. introduce face shortest-path tree 3. how to enumerate shellings}

>>>>

We compare the reference Neumann eigenvalues with the gradient potential estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
A brufe-force search easily enumerates all the (reptition-free) face-paths between triangles, which allows us to find the best estimate possible estimate with the aforementioned theorem.

We compare the reference Neumann and Dirichlet eigenvalues with the bounds computed in Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
Here, we take into account Lemma~\ref{lemma:volumecomparison} and Theorem~\ref{proposition:starreflection} (with Remark~\ref{remark:improved_starreflection}).
Again, brute-force search is feasible to enumerate all possible shellings of moderately small two-dimensional triangulations,
allowing us to compute the best possible of these bounds.

@@

The reference Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators are found via standard finite element eigenvalue computations, using the lowest-order finite element de~Rham complex over a sufficiently refined mesh (four steps of uniform refinement).
Again, we compare these reference values with estimates obtained Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}, and in the special case of the gradient, with Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.

The computation becomes more demanding in dimension three. 
Enumerating all the paths between tetrahedra in our example triangulations is feasible but takes considerably longer. 
Brute-force enumeration of all shellings seems infeasible, though. 
Instead,

\todo{How to select shellings}
